Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-10-03 grove-paper.tex
Fix vertex and edge numbering in (most) figures (Michael D. Adams)

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
TODO
\caption{User interface}
\label{fig:A simple tree with a hole-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Root$_{1}$"] -> {
   "$\texttt{x}_{4}$" [> "L$_{3}$"],
   {}
  }
 }
};
\end{tikzpicture}
\caption{Graph representation}
\label{fig:A simple tree with a hole-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole}
\label{fig:A simple tree with a hole}
\end{figure}

@@

\begin{figure}
% TODO: naive add that creates a conflict
% \begin{tikzpicture}
% \path (0,0)       node {\includegraphics[scale=0.4]{graphviz/wrapping/1.dot}};
% \path (0cm,-4cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/2.dot}};
% \path (0cm,-8cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/3.dot}};
% \path (0cm,-12cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/4.dot}};
% \path (0cm,-16cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/5.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (-0.5,-3cm) graph[graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{3}$"'],
  "$\texttt{z}_{6}$" [> "R$_{5}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Change-b} after deleting \Edge{1}}
\label{fig:Wrapping-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"]
 }
};
\path (-0.5cm,-3cm) graph[graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{5}$"'],
  "$\texttt{z}_{6}$" [> "R$_{5}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Wrapping-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{9}$"'] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{z}_{6}$" [> "R$_{5}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-b} after adding \Edge{9}}
\label{fig:Wrapping-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Wrapping}
\label{fig:Wrapping}
\end{figure}

@@

\begin{figure}
% \centering
% \begin{tikzpicture}
% \path (0,0)    node {\includegraphics[scale=0.75]{graphviz/move/1.dot}};
% \path (0,-5cm) node {\includegraphics[scale=0.75]{graphviz/move/2.dot}};
% \path (0,-9cm) node {\includegraphics[scale=0.75]{graphviz/move/3.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"]
 }
};
\path (0cm,-3cm) graph [graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{3}$"'],
  "$\texttt{z}_{6}$" [> "R$_{5}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-c} after deleting \Edge{9}}
\label{fig:Move-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.45\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{11}$"] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{z}_{6}$" [> "R$_{5}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-a} after adding \Edge{11}}
\label{fig:Move-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Moving \Vertex{2} from the left child to the right child of \Vertex{8}}
\label{fig:Move}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{11}$"] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{z}_{6}$" [> "R$_{5}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Alice replaces \Vertex{4} with \Vertex{12}}
\label{fig:Editing Different Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{11}$"] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{v}_{14}$" [> "R$_{15}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Bob replaces \Vertex{6} with \Vertex{14}}
\label{fig:Editing Different Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{11}$"] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{v}_{14}$" [> "R$_{15}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Different Parts of the Code-a} with \autoref{fig:Editing Different Parts of the Code-b}}
\label{fig:Editing Different Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code}
\label{fig:Editing Different Parts of the Code}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{11}$"] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{w}_{16}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Different Parts of the Code-c} after Alice replaces \Vertex{14} with \Vertex{16}}
\label{fig:Editing Nested Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{v}_{14}$" [> "R$_{15}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Different Parts of the Code-c} after Bob move \Vertex{2} to the left child of \Vertex{8}}
\label{fig:Editing Nested Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{w}_{16}$" [> "R$_{17}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}}
\label{fig:Editing Nested Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code}
\label{fig:Editing Nested Parts of the Code}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{w}_{16}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{20}$" [> "R$_{21}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{w}_{16}$" [> "R$_{17}$"]
   },
   "$\texttt{y}_{22}$" [> "R$_{23}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{w}_{16}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{20}$" [> "R$_{21}$"],
    "$\texttt{y}_{22}$" [> "R$_{23}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
TODO: show UI
\caption{User interface showing the multi-child conflict in \autoref{fig:Multi-child-d}}
\label{fig:Multi-child-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{+}_{24}$" [> "L$_{23}$"'] -> {
    "$\texttt{x}_{26}$" [> "L$_{25}$"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}

TODO: use * and +

TODO: UI (at least moc up)
\caption{Initial code}
\label{fig:Multi-parent-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{+}_{24}$" [> "L$_{23}$"'],
   "$\texttt{x}_{26}$" [> "R$_{27}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-parent-a} after Alice ... TODO}
\label{fig:Multi-parent-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{+}_{24}$" [> "L$_{23}$"'] -> {
    {},
    "$\texttt{x}_{26}$" [> "R$_{29}$"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-child-a} after Bob ... TODO}
\label{fig:Multi-parent-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{$\texttt{+}_{8}$} [> "Root$_{7}$"] -> {
   "$\texttt{+}_{24}$" [> "L$_{23}$"'] -> {
    {},
    b/"$\texttt{x}_{26}$" [> "R$_{29}$"']
   },
   {}
  }
 },
};
\path [edge style,->] (a) to ["R$_{27}$",out=-60,in=60] (b);
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-parent-b} with \autoref{fig:Multi-parent-c}}
\label{fig:Multi-parent-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts}
\label{fig:Multi-parent}
\end{figure*}

>>>>

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
TODO
\caption{User interface}
\label{fig:A simple tree with a hole-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Root$_{1}$"] -> {
   "$\texttt{x}_{4}$" [> "L$_{3}$"'],
   {}
  }
 }
};
\end{tikzpicture}
\caption{Graph representation}
\label{fig:A simple tree with a hole-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole}
\label{fig:A simple tree with a hole}
\end{figure}

@@

\begin{figure}
% TODO: naive add that creates a conflict
% \begin{tikzpicture}
% \path (0,0)       node {\includegraphics[scale=0.4]{graphviz/wrapping/1.dot}};
% \path (0cm,-4cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/2.dot}};
% \path (0cm,-8cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/3.dot}};
% \path (0cm,-12cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/4.dot}};
% \path (0cm,-16cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/5.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (-0.5,-3cm) graph[graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{3}$"'],
  "$\texttt{z}_{8}$" [> "R$_{7}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Change-b} after deleting \Edge{1}}
\label{fig:Wrapping-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"]
 }
};
\path (-0.5cm,-3cm) graph[graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{5}$"'],
  "$\texttt{z}_{8}$" [> "R$_{7}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Wrapping-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{11}$"'] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{z}_{8}$" [> "R$_{7}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-b} after adding \Edge{9}}
\label{fig:Wrapping-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Wrapping}
\label{fig:Wrapping}
\end{figure}

@@

\begin{figure}
% \centering
% \begin{tikzpicture}
% \path (0,0)    node {\includegraphics[scale=0.75]{graphviz/move/1.dot}};
% \path (0,-5cm) node {\includegraphics[scale=0.75]{graphviz/move/2.dot}};
% \path (0,-9cm) node {\includegraphics[scale=0.75]{graphviz/move/3.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"]
 }
};
\path (0cm,-3cm) graph [graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{3}$"'],
  "$\texttt{z}_{8}$" [> "R$_{7}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-c} after deleting \Edge{9}}
\label{fig:Move-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.45\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{13}$"] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{z}_{6}$" [> "R$_{7}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-a} after adding \Edge{11}}
\label{fig:Move-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Moving \Vertex{2} from the left child to the right child of \Vertex{8}}
\label{fig:Move}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{13}$"] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{z}_{6}$" [> "R$_{7}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Alice replaces \Vertex{4} with \Vertex{12}}
\label{fig:Editing Different Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{13}$"] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Bob replaces \Vertex{6} with \Vertex{14}}
\label{fig:Editing Different Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{13}$"] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Different Parts of the Code-a} with \autoref{fig:Editing Different Parts of the Code-b}}
\label{fig:Editing Different Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code}
\label{fig:Editing Different Parts of the Code}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{13}$"] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice replaces \Vertex{14} with \Vertex{16}}
\label{fig:Editing Nested Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob move \Vertex{2} to the left child of \Vertex{8}}
\label{fig:Editing Nested Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}}
\label{fig:Editing Nested Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code}
\label{fig:Editing Nested Parts of the Code}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{22}$" [> "R$_{21}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   "$\texttt{y}_{24}$" [> "R$_{23}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{22}$" [> "R$_{21}$"],
    "$\texttt{y}_{24}$" [> "R$_{23}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
TODO: show UI
\caption{User interface showing the multi-child conflict in \autoref{fig:Multi-child-d}}
\label{fig:Multi-child-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
TODO: UI (at least moc up)
\caption{Initial code}
\label{fig:Multi-parent-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{w}_{20}$" [> "R$_{25}$"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-parent-a} after Alice ... TODO}
\label{fig:Multi-parent-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'],
   "$\texttt{w}_{20}$" [> "R$_{27}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-child-a} after Bob ... TODO}
\label{fig:Multi-parent-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{$\texttt{+}_{10}$} [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    b/"$\texttt{w}_{20}$" [> "R$_{25}$"']
   },
   {}
  }
 },
};
\path [edge style,->] (a) to ["R$_{27}$",out=-60,in=60] (b);
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-parent-b} with \autoref{fig:Multi-parent-c}}
\label{fig:Multi-parent-d}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   v2/"$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{w}_{20}$" [> "R$_{25}$"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code TODO: move to previous figure}
\label{fig:Multi-parent-e}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts}
\label{fig:Multi-parent}
\end{figure*}
